### 2020-04-05 07-discussion.tex
small adjustments

Our encoding increases the expressivity of  RS  concerning:
%the behaviour of the context,
the possibility of alternative behaviour of
mutated entities, and  the communication between two different Reaction Systems.
It is important to note that our encoding guarantees that from each state, 
in the  c\CNA \ transition system, only one transition comes out, 
as the dynamics is totally deterministic.

@@

\subsection{Mutating entities} 
In RS, when an entity is present, it can potentially be involved in each reactions where it is required.
With a few more lines of code, in c\CNA~it is possible to describe the behaviour of a mutation of 
an entity, in a way that the mutated version of the entity can take 
part to only a subset of the rules requiring  the  \emph{normal version} of the entity.
For example, let us assume that entity $s1$ is consumed by reactions $a1$ and $a2$.
Reaction $a1$ produces also $s1$ if $s2$ is present, otherwise $a1$ produces a mutated version of $s1$, 
say $s1'$.
When $s1'$ is produced, reaction $a2$ behaves in the same way as if $s1$ would be absent, whereas $a2$
recognises the presence of $s1'$ and behaves in the same way as if $s1$ would be present.
Technically, in both cases it is enough to add one more non 
deterministic choice in the code of $P_{a1}$ and $P_{a2}$.

@@

\begin{table}[t]
\centering
\begin{tabular}{|c|c|}
\hline
$rs1$  & $rs2$ \\
\hline
%$r1_1=(s1,\ , s2)$ & $r2_1=(s3,\  ,s1)$\\
$a_1=(s,\ , x)$ & $a_2=(y,\  ,s)$\\
%$r1_2=(\ , s2,s1)$ & $r2_2=(s1,\ ,s3)$\\
\hline 
\end{tabular}
\caption{The two Reaction Systems $rs1$ and $rs2$.}
\label{tab:rules}
\end{table}
 \noindent
Now, we set our example such that the two contexts, for  $rs1$ and $rs2$, do not provide any entities.
We also assume that entity $s$ in $rs1$ is provided by $rs2$, as $rs2$ produces a quantity of $s$ that is enough for $rs1$ and $rs2$.
For technical reasons, we can not use the same name for  $s$ in both the two RSs, then we use the name $ss$ in $rs2$.
%
We need to modify our translation technique to suite this new setting. 
As we do not model contexts, we introduce  \emph{dummy} channel names $dx$ and $dss$ to model the absence of entities. Also, thanks to the simplicity of the example, we can leave out the use of the   $p_i$ channels. This streamlining does not affect the programming technique we propose to make two RSs communicate.
%Thus, there will be no $Cxt$ processes and we manage the code in a way that $rs1$ will receive the entity $s1$ from $rs2$. 
%Please also note that, for our simple example, we do not have anymore to specify the all steps
%of a interactive system, as the communication mechanism from $rs2$ to $rs1$ will generate an infinite
%behaviour.
%\noindent
%First, we translate the rules in $rs1$:
First, we translate the reaction in $rs1$:
\[
\begin{array}{lcl}
%\llbracket r1_1\rrbracket \defeq P_{r1_1}&\defeq &\startchain{\silent}\chainedlink{s1}{\noact}\chainedlink{\noact}{s1}\chainedlink{\tilde{s2}}{\noact}\chainedlink{\noact}{\tilde{s2}}\chainend{r1_2}.P_{r1_1} +
%\startchain{\silent}\chainedlink{\overline{s1}}{\noact}\chainedlink{\noact}{\overline{s1}}\chainend{r1_2}.P_{r1_1}\\
\llbracket a_1\rrbracket \defeq P_{a_1}&\defeq &
\startchain{\silent}\chainedlink{s_i}{{\color{blue}\noact}}\chainedlink{{\color{blue}\noact}}{s_o}\chainedlink{\tilde{x}_i}{{\color{gray}\noact}}\chainedlink{{\color{gray}\noact}}{\tilde{x}_o}\chainend{a_2}.P_{a_1} +
\startchain{\silent}\chainedlink{\overline{s}_i}{\noact}\chainedlink{\noact}{\overline{s}_o}    \chainedlink{dx_i}{\noact}\chainedlink{\noact}{dx_o}\chainend{a_2}.P_{a_1}\\
%\end{array}
%\]
%\\
%
%\begin{array}{lcl}
%\llbracket r1_2\rrbracket \defeq P_{r1_2}&\defeq &\startchain{r1_2}\chainedlink{\overline{s2}}{\noact}\chainedlink{\noact}{\overline{s2}}\chainedlink{\tilde{s1}}{\noact}\chainedlink{\noact}{\tilde{s1}}\chainend{r2_1}.P_{r2_1} +
%\startchain{r1_2}\chainedlink{s2}{\noact}\chainedlink{\noact}{s2}\chainend{r2_1}.P_{r2_1}\\
\end{array}
\]

\noindent
Please note, that prefixes of process $P_{a_1}$ end with the channel name $a_2$, as the link chain is now connected with the  reaction of  $rs2$.
The translation for the entities follows.
\[
\begin{array}{lclcl}
\llbracket s \rrbracket &\defeq &P_{s} &\defeq & \startchain{{\color{blue}s_i}}\chainedlink{{\color{blue}s_o}}{\noact}\chainedlink{\noact}{{\color{blue}\widehat{s}_i}}\chainend{{\color{blue}\widehat{s}_o}}.P_{s} + \startchain{s_i}\chainend{s_o}.\overline{P_{s}}\\
&& \overline{P_{s}}&\defeq &\startchain{\overline{s}_i}\chainedlink{\overline{s}_o}{\noact}\chainedlink{\noact}{\widehat{s}_i}\chainend{\widehat{s}_o}.P_{s}+\startchain{\overline{s}_i}\chainend{\overline{s}_i}.\overline{P_{s}}\\
%\begin{array}{lclclll}
\llbracket x \rrbracket &\defeq & P_{x}& \defeq &\startchain{\tilde{x}_i}\chainend{\tilde{x}_o}.P_{x} +  \startchain{dx_i}\chainend{dx_o}.\overline{P_{x}}\\
%\\
%&&\overline{P_{s2}}&\defeq &\startchain{\overline{s2}}\chainedlink{\overline{s2}}{\noact}\chainedlink{\noact}{\tilde{s2}}\chainend{\tilde{s2}}.P_{s2} +
%\startchain{\overline{s2}}\chainend{\overline{s2}}.\overline{P_{s2}}\\
%\\
%\\
&& \overline{P_{x}}&\defeq &\startchain{{\color{gray}\tilde{x}_i}}\chainend{{\color{gray}\tilde{x}_o}}.P_{x} +  \startchain{dx_i}\chainend{dx_o}.\overline{P_{x}}\\
%\end{array}
%\]
%
%\[

@@

%\[
%\begin{array}{lclclll}
%\llbracket s2 \rrbracket &\defeq& P_{s2}&\defeq &\startchain{s2}\chainedlink{s2}{\noact}\chainedlink{\noact}{\tilde{s2}}\chainend{\tilde{s2}}.P_{s2} +  \startchain{s2}\chainend{s2}.\overline{P_{s2}}\\
%%\\
%&&\overline{P_{s2}}&\defeq &\startchain{\overline{s2}}\chainedlink{\overline{s2}}{\noact}\chainedlink{\noact}{\tilde{s2}}\chainend{\tilde{s2}}.P_{s2} +
%\startchain{\overline{s2}}\chainend{\overline{s2}}.\overline{P_{s2}}\\
%
%\end{array}
%\]

@@

\[
\begin{array}{lcl}
\llbracket a_2\rrbracket \defeq P_{a_2}&\defeq &\startchain{a_2}\chainedlink{y_i}{{\color{gray}\noact}}\chainedlink{{\color{gray}\noact}}{y_o}\chainedlink{\tilde{ss}_i}{{\color{red}\noact}}\chainedlink{{\color{red}\noact}}{\tilde{ss}_o}\chainend{\silent}.P_{a_2}+
\startchain{a_2}\chainedlink{\overline{y}_i}{\noact}\chainedlink{\noact}{\overline{y}_o}    
\chainedlink{dss_i}{\noact}\chainedlink{\noact}{dss_o}\chainend{\silent}.P_{a_2}\\
%\end{array}
%\]
%
%\[
%\begin{array}{lcl}
%\llbracket r2_2\rrbracket \defeq P_{r2_2}&\defeq &\startchain{r2_2}\chainedlink{ss1}{\noact}\chainedlink{\noact}{ss1}\chainedlink{\tilde{s3}}{\noact}\chainedlink{\noact}{\tilde{s3}}\chainend{\silent}.P_{r2_2}
%+
%\startchain{r2_2}\chainedlink{\overline{ss1}}{\noact}\chainedlink{\noact}{\overline{ss1}}\chainend{\silent}.P_{r2_2}\\
\end{array}
\]
\noindent
In the translation of the entities in  $rs2$, we introduce the mechanism that allows the entity
$s$ ($ss$ in $rs2$) to be provided in $rs1$. Every time $ss$ is produced in $rs2$,  a virtual link is
created to synchronise with $rs1$   on link $\link{\widehat{s}_i}{\widehat{s}_o}$:
\[
\begin{array}{lclcl}
\llbracket ss \rrbracket& \defeq& P_{ss}&\defeq &\startchain{\tilde{ss}_i}\chainedlink{\widehat{s}_i}{\noact}\chainedlink{\noact}{\widehat{s}_o}\chainend{\tilde{ss}_o}.P_{ss}+
\startchain{dss_i}   \chainend{dss_o}.\overline{P_{ss}} \\

%\end{array}
%\]
%\[
%\begin{array}{lcllcl}
&&\overline{P_{ss}}&\defeq &\startchain{{\color{red}\tilde{ss}_i}}\chainedlink{{\color{red}\widehat{s}_i}}{{\color{blue}\noact}}\chainedlink{{\color{blue}\noact}}{{\color{red}\widehat{s}_o}}\chainend{{\color{red}\tilde{ss}_o}}.P_{ss}
+
\startchain{dss_i}\chainend{dss_o}.\overline{P_{ss}}\\
\llbracket y\rrbracket&\defeq & P_{y}&\defeq &\startchain{{\color{gray}y_i}}\chainend{{\color{gray}y_o}}.\overline{P_{y}} \\
&&\overline{P_{y}}&\defeq &
%\startchain{\overline{y}_i}\chainedlink{\overline{y}_o}{\noact}\chainedlink{\noact}{\tilde{y}_i}\chainend{\tilde{y}_o}.P_{y}
%+ 
\startchain{\overline{y}_i}\chainend{\overline{y}_o}.\overline{P_{y}}
\end{array}
\]
%\[
%\begin{array}{lcllcl}

@@

\noindent
We now assume that the initial system is $S \defeq \restrict{names}(P_{a_1}|P_{a_2}|P_s|P_y|\overline{P_x}|\overline{P_{ss}})$, i.e.
only entities $s$ and $y$ are present. Now, the only possible transition has  the following label (that we report without restriction):
\[
\startchain{\silent}\chainedlink{s_i}{{\color{blue}s_i}}\chainedlink{{\color{blue}s_o}}{s_o}\chainedlink{\tilde{x}_i}{{\color{gray}\tilde{x}_i}}\chainedlink{{\color{gray}\tilde{x}_o}}{\tilde{x}_o} \chainedlink{a_2}{a_2}\chainedlink{y_i}{ {\color{gray}y_i}}\chainedlink{{\color{gray}y_o}}{y_o}\chainedlink{\tilde{ss}_i}{{\color{red}\tilde{ss}_i}}
\chainedlink{{\color{red}\widehat{s}_i}}{{\color{blue}\widehat{s}_i}}
\chainedlink{{\color{blue}\widehat{s}_o}}{{\color{red}\widehat{s}_o}}
\chainedlink{{\color{red}\tilde{ss}_o}}{\tilde{ss}_o}\chainend{\silent},
\]
where the black links belong to the prefixes of $P_{a_1}$, and $P_{a_2}$, the blue links belong to $P_s$, the gray links belong to $P_y$, and $\overline{P_x}$ and the red links belong to $\overline{P_{ss}}$.
After the execution, the entity $s$ is still present in $rs1$ as it has been provided by $rs2$.\\

>>>>

Our encoding increases the expressivity of  RS  concerning:
%the behaviour of the context,
the possibility of alternative behaviour of
mutated entities, and  the communication between two different Reaction Systems.
It is important to note that, when the context is deterministic, our encoding guarantees that from each state, 
in the  c\CNA \ transition system, only one state is reachable, 
as the dynamics is totally deterministic.

@@

\subsection{Mutating entities} 
In RS, when an entity is present, it can potentially be involved in each reactions where it is required.
With a few more lines of code, in c\CNA~it is possible to describe the behaviour of a mutation of 
an entity, in a way that the mutated version of the entity can take 
part to only a subset of the rules requiring  the  \emph{normal version} of the entity.
For example, let us assume that entity $s1$ is consumed by reactions $a1$ and $a2$.
Reaction $a1$ produces also $s1$ if $s2$ is present, otherwise $a1$ produces a mutated version of $s1$, 
say $s1'$.
When $s1'$ is produced, reaction $a2$ behaves in the same way as if $s1$ would be absent, whereas $a2$
recognises the presence of $s1'$ and behaves in the same way as if $s1$ would be present.
Technically, in both cases it is enough to add one more nondeterministic choice in the code of $P_{a1}$ and $P_{a2}$.

@@

\begin{table}[t]
\centering
\begin{tabular}{|c|c|}
\hline
$rs1$  & $rs2$ \\
\hline
%$r1_1=(s1,\ , s2)$ & $r2_1=(s3,\  ,s1)$\\
$a_1=(s,\ , x)$ & $a_2=(y,\  ,s)$\\
%$r1_2=(\ , s2,s1)$ & $r2_2=(s1,\ ,s3)$\\
\hline 
\end{tabular}
\caption{The two Reaction Systems $rs1$ and $rs2$.}
\label{tab:rules}
\end{table}
 \noindent
Now, we set our example such that the two contexts, for  $rs1$ and $rs2$, do not provide any entities.
We also assume that entity $s$ in $rs1$ is provided by $rs2$, as $rs2$ produces a quantity of $s$ that is enough for $rs1$ and $rs2$.
For technical reasons, we can not use the same name for  $s$ in both the two RSs, then we use the name $ss$ in $rs2$.
%
We need to modify our translation technique to suite this new setting. 
As we do not model contexts, we introduce  \emph{dummy} channel names $dx$ and $dss$ to model the absence of entities. Also, thanks to the simplicity of the example, we can leave out the use of the   $p_i$ channels. This streamlining does not affect the programming technique we propose to make two RSs communicate.
%Thus, there will be no $Cxt$ processes and we manage the code in a way that $rs1$ will receive the entity $s1$ from $rs2$. 
%Please also note that, for our simple example, we do not have anymore to specify the all steps
%of a interactive system, as the communication mechanism from $rs2$ to $rs1$ will generate an infinite
%behaviour.
%\noindent
%First, we translate the rules in $rs1$:
First, we translate the reaction in $rs1$:
\[
\begin{array}{lcl}
%\llbracket r1_1\rrbracket \defeq P_{r1_1}&\defeq &\startchain{\silent}\chainedlink{s1}{\noact}\chainedlink{\noact}{s1}\chainedlink{\widetilde{s2}}{\noact}\chainedlink{\noact}{\widetilde{s2}}\chainend{r1_2}.P_{r1_1} +
%\startchain{\silent}\chainedlink{\overline{s1}}{\noact}\chainedlink{\noact}{\overline{s1}}\chainend{r1_2}.P_{r1_1}\\
\llbracket a_1\rrbracket \defeq P_{a_1}&\defeq &
\startchain{\silent}\chainedlink{s_i}{{\color{blue}\noact}}\chainedlink{{\color{blue}\noact}}{s_o}\chainedlink{\widetilde{x}_i}{{\color{gray}\noact}}\chainedlink{{\color{gray}\noact}}{\widetilde{x}_o}\chainend{a_2}.P_{a_1} +
\startchain{\silent}\chainedlink{\overline{s}_i}{\noact}\chainedlink{\noact}{\overline{s}_o}    \chainedlink{dx_i}{\noact}\chainedlink{\noact}{dx_o}\chainend{a_2}.P_{a_1}\\
%\end{array}
%\]
%\\
%
%\begin{array}{lcl}
%\llbracket r1_2\rrbracket \defeq P_{r1_2}&\defeq &\startchain{r1_2}\chainedlink{\overline{s2}}{\noact}\chainedlink{\noact}{\overline{s2}}\chainedlink{\widetilde{s1}}{\noact}\chainedlink{\noact}{\widetilde{s1}}\chainend{r2_1}.P_{r2_1} +
%\startchain{r1_2}\chainedlink{s2}{\noact}\chainedlink{\noact}{s2}\chainend{r2_1}.P_{r2_1}\\
\end{array}
\]

\noindent
Please note, that prefixes of process $P_{a_1}$ end with the channel name $a_2$, as the link chain is now connected with the  reaction of  $rs2$.
The translation for the entities follows.
\[
\begin{array}{lclcl}
\llbracket s \rrbracket &\defeq &P_{s} &\defeq & \startchain{{\color{blue}s_i}}\chainedlink{{\color{blue}s_o}}{\noact}\chainedlink{\noact}{{\color{blue}\widehat{s}_i}}\chainend{{\color{blue}\widehat{s}_o}}.P_{s} + \startchain{s_i}\chainend{s_o}.\overline{P_{s}}\\
&& \overline{P_{s}}&\defeq &\startchain{\overline{s}_i}\chainedlink{\overline{s}_o}{\noact}\chainedlink{\noact}{\widehat{s}_i}\chainend{\widehat{s}_o}.P_{s}+\startchain{\overline{s}_i}\chainend{\overline{s}_i}.\overline{P_{s}}\\
%\begin{array}{lclclll}
\llbracket x \rrbracket &\defeq & P_{x}& \defeq &\startchain{\widetilde{x}_i}\chainend{\widetilde{x}_o}.P_{x} +  \startchain{dx_i}\chainend{dx_o}.\overline{P_{x}}\\
%\\
%&&\overline{P_{s2}}&\defeq &\startchain{\overline{s2}}\chainedlink{\overline{s2}}{\noact}\chainedlink{\noact}{\widetilde{s2}}\chainend{\widetilde{s2}}.P_{s2} +
%\startchain{\overline{s2}}\chainend{\overline{s2}}.\overline{P_{s2}}\\
%\\
%\\
&& \overline{P_{x}}&\defeq &\startchain{{\color{gray}\widetilde{x}_i}}\chainend{{\color{gray}\widetilde{x}_o}}.P_{x} +  \startchain{dx_i}\chainend{dx_o}.\overline{P_{x}}\\
%\end{array}
%\]
%
%\[

@@

%\[
%\begin{array}{lclclll}
%\llbracket s2 \rrbracket &\defeq& P_{s2}&\defeq &\startchain{s2}\chainedlink{s2}{\noact}\chainedlink{\noact}{\widetilde{s2}}\chainend{\widetilde{s2}}.P_{s2} +  \startchain{s2}\chainend{s2}.\overline{P_{s2}}\\
%%\\
%&&\overline{P_{s2}}&\defeq &\startchain{\overline{s2}}\chainedlink{\overline{s2}}{\noact}\chainedlink{\noact}{\widetilde{s2}}\chainend{\widetilde{s2}}.P_{s2} +
%\startchain{\overline{s2}}\chainend{\overline{s2}}.\overline{P_{s2}}\\
%
%\end{array}
%\]

@@

\[
\begin{array}{lcl}
\llbracket a_2\rrbracket \defeq P_{a_2}&\defeq &\startchain{a_2}\chainedlink{y_i}{{\color{gray}\noact}}\chainedlink{{\color{gray}\noact}}{y_o}\chainedlink{\widetilde{ss}_i}{{\color{red}\noact}}\chainedlink{{\color{red}\noact}}{\widetilde{ss}_o}\chainend{\silent}.P_{a_2}+
\startchain{a_2}\chainedlink{\overline{y}_i}{\noact}\chainedlink{\noact}{\overline{y}_o}    
\chainedlink{dss_i}{\noact}\chainedlink{\noact}{dss_o}\chainend{\silent}.P_{a_2}\\
%\end{array}
%\]
%
%\[
%\begin{array}{lcl}
%\llbracket r2_2\rrbracket \defeq P_{r2_2}&\defeq &\startchain{r2_2}\chainedlink{ss1}{\noact}\chainedlink{\noact}{ss1}\chainedlink{\widetilde{s3}}{\noact}\chainedlink{\noact}{\widetilde{s3}}\chainend{\silent}.P_{r2_2}
%+
%\startchain{r2_2}\chainedlink{\overline{ss1}}{\noact}\chainedlink{\noact}{\overline{ss1}}\chainend{\silent}.P_{r2_2}\\
\end{array}
\]
\noindent
In the translation of the entities in  $rs2$, we introduce the mechanism that allows the entity
$s$ ($ss$ in $rs2$) to be provided in $rs1$. Every time $ss$ is produced in $rs2$,  a virtual link is
created to synchronise with $rs1$   on link $\link{\widehat{s}_i}{\widehat{s}_o}$:
\[
\begin{array}{lclcl}
\llbracket ss \rrbracket& \defeq& P_{ss}&\defeq &\startchain{\widetilde{ss}_i}\chainedlink{\widehat{s}_i}{\noact}\chainedlink{\noact}{\widehat{s}_o}\chainend{\widetilde{ss}_o}.P_{ss}+
\startchain{dss_i}   \chainend{dss_o}.\overline{P_{ss}} \\

%\end{array}
%\]
%\[
%\begin{array}{lcllcl}
&&\overline{P_{ss}}&\defeq &\startchain{{\color{red}\widetilde{ss}_i}}\chainedlink{{\color{red}\widehat{s}_i}}{{\color{blue}\noact}}\chainedlink{{\color{blue}\noact}}{{\color{red}\widehat{s}_o}}\chainend{{\color{red}\widetilde{ss}_o}}.P_{ss}
+
\startchain{dss_i}\chainend{dss_o}.\overline{P_{ss}}\\
\llbracket y\rrbracket&\defeq & P_{y}&\defeq &\startchain{{\color{gray}y_i}}\chainend{{\color{gray}y_o}}.\overline{P_{y}} \\
&&\overline{P_{y}}&\defeq &
%\startchain{\overline{y}_i}\chainedlink{\overline{y}_o}{\noact}\chainedlink{\noact}{\widetilde{y}_i}\chainend{\widetilde{y}_o}.P_{y}
%+ 
\startchain{\overline{y}_i}\chainend{\overline{y}_o}.\overline{P_{y}}
\end{array}
\]
%\[
%\begin{array}{lcllcl}

@@

\noindent
We now assume that the initial system is $S \defeq \restrict{names}(P_{a_1}|P_{a_2}|P_s|P_y|\overline{P_x}|\overline{P_{ss}})$, i.e.
only entities $s$ and $y$ are present. Now, the only possible transition has  the following label (that we report without restriction):
\[
\startchain{\silent}\chainedlink{s_i}{{\color{blue}s_i}}\chainedlink{{\color{blue}s_o}}{s_o}\chainedlink{\widetilde{x}_i}{{\color{gray}\widetilde{x}_i}}\chainedlink{{\color{gray}\widetilde{x}_o}}{\widetilde{x}_o} \chainedlink{a_2}{a_2}\chainedlink{y_i}{ {\color{gray}y_i}}\chainedlink{{\color{gray}y_o}}{y_o}\chainedlink{\widetilde{ss}_i}{{\color{red}\widetilde{ss}_i}}
\chainedlink{{\color{red}\widehat{s}_i}}{{\color{blue}\widehat{s}_i}}
\chainedlink{{\color{blue}\widehat{s}_o}}{{\color{red}\widehat{s}_o}}
\chainedlink{{\color{red}\widetilde{ss}_o}}{\widetilde{ss}_o}\chainend{\silent},
\]
where the black links belong to the prefixes of $P_{a_1}$, and $P_{a_2}$, the blue links belong to $P_s$, the gray links belong to $P_y$, and $\overline{P_x}$ and the red links belong to $\overline{P_{ss}}$.
After the execution, the entity $s$ is still present in $rs1$ as it has been provided by $rs2$.\\

### 2020-04-05 09-appendix.tex
small adjustments

Otherwise, let $\mathcal{Q}\defeq \{Q'~\mid~\exists w.\ Q\xRightarrow{w}Q' \ \wedge\ w\entails F\}$ be the set of processes reachable from $Q$ via a transition with a (complete) label that satisfies $F$. Since our processes are with guarded recursion, the set $\mathcal{Q}$ is finite. Let $\mathcal{Q} = \{Q'_1,...,Q'_n\}$. By hypothesis all processes in $\mathcal{Q}$ must not be bio-logically equivalent to $P'$, hence for any $i\in[1,n]$ there exists a bioHML formula $G_i$ such that $P'\entails G_i$ and $Q'_i\not\entails G_i$ (if it was the opposite, $P'\not\entails G_i$ and $Q'_i\entails G_i$, we can use the converse formulas). But then the formula $G\defeq \langle F\rangle(G_1\wedge\dots\wedge G_n)$ is such that $P\entails G$ and $Q\not\entails G$, contradicting the assumption $P\equiv_{\mathcal{L}_F} Q$.

\item
If $\upsilon \not\entails F$ then the proof is analogous to the previous case and thus omitted.
\end{itemize}
\end{description}
\end{proof}

>>>>

Otherwise, let $\mathcal{Q}\defeq \{Q'~\mid~\exists w.\ Q\xRightarrow{w}Q' \ \wedge\ w\entails F\}$ be the set of processes reachable from $Q$ via a transition with a (complete) label that satisfies $F$. Since our processes are with guarded recursion, the set $\mathcal{Q}$ is finite. Let $\mathcal{Q} = \{Q'_1,...,Q'_n\}$. By hypothesis all processes in $\mathcal{Q}$ must not be bio-logically equivalent to $P'$, hence for any $i\in[1,n]$ there exists a bioHML formula $G_i$ such that $P'\entails G_i$ and $Q'_i\not\entails G_i$ (if it was the opposite, $P'\not\entails H_i$ and $Q'_i\entails H_i$ for some $H_i$, we can use the converse formula $G_i\defeq \overline{H}_i$). But then the formula $G\defeq \langle F\rangle(G_1\wedge\dots\wedge G_n)$ is such that $P\entails G$ and $Q\not\entails G$, contradicting the assumption $P\equiv_{\mathcal{L}_F} Q$.

\item
If $\upsilon \not\entails F$ then the proof is analogous to the previous case (by exploiting $\neg F$) and thus omitted.
\end{itemize}
\end{description}
\end{proof}
